Manuscript for Markup Language course - Using bayesian statistics to prove

### 2022-01-24 manuscript_inan.Rmd
edited plot titles

---
title: Manuscript for Markup Language course - Using bayesian statistics to prove
  a point
author: "Inan Bostanci"
date: "1/15/2022"
output:
  pdf_document: default
  html_document: default
---

>>>>

---
title: Manuscript for Markup Language course - Using bayesian statistics to prove
  a point
author: "Inan Bostanci"
date: "1/15/2022"
output:
  html_document: default
  pdf_document: default
---
